\documentclass[a4paper,10pt]{article}

\usepackage[left=0.7in,right=0.7in,top=0.7in,bottom=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}

\begin{document}

%-------------------- HEADER --------------------
\begin{center}
    {\Huge \textbf{SENAATH SURAWEERA}}\\
    \vspace{4pt}
    \small Computer Science Undergraduate \\
    \vspace{6pt}
    \href{mailto:senaathsuraweera2003@gmail.com}{senaathsuraweera2003@gmail.com} \quad | \quad +94 705216508 \\
    Battaramulla, Sri Lanka \quad | \quad 
    \href{https://www.linkedin.com/in/senaath-suraweera}{linkedin.com/in/senaath-suraweera}
\end{center}

\vspace{8pt}

%-------------------- PROFILE --------------------
\section*{Profile}
Motivated Computer Science undergraduate with a strong foundation in software development, problem-solving, and system design. Experienced in developing full-stack applications and academic projects using modern technologies. Passionate about building scalable solutions and continuously learning emerging technologies.

%-------------------- EDUCATION --------------------
\section*{Education}

\textbf{University of Colombo School of Computing} \hfill \textit{Present}\\
B.Sc. (General) in Computer Science

\textbf{Informatics Institute of Technology} \hfill \textit{Present}\\
B.Sc. (Hons) in Computer Science

\textbf{Mahanama College, Colombo} \hfill \textit{2009 -- 2023}\\
GCE A/L (Mathematics): 2A, 1B \\
GCE O/L: 9A

%-------------------- PROJECTS --------------------
\section*{Projects}

\textbf{RideMachan (Java, JavaScript, HTML/CSS)} \hfill \href{https://github.com/Senaath-Suraweera/RideMachan}{GitHub}
\begin{itemize}
    \item Built a full-stack ride request management web application where users can submit requests and drivers can accept and manage them.
    \item Implemented backend logic in Java with a clean HTML/CSS/JavaScript frontend interface.
\end{itemize}

\textbf{Recursive Descent Parser with Integrated Interpreter (C)} \hfill \href{https://github.com/Senaath-Suraweera/Recursive-Descent-Parser-with-Integrated-Interpreter}{GitHub}
\begin{itemize}
    \item Hand-wrote a recursive descent parser and interpreter in C without any parser-generator tooling.
    \item Parses and evaluates arithmetic and logical expressions by walking a grammar rule set.
\end{itemize}

\textbf{Get APOD (Java, JavaFX)} \hfill \href{https://github.com/Senaath-Suraweera/Get-APOD}{GitHub}
\begin{itemize}
    \item Developed a JavaFX desktop application that fetches and displays NASA's Astronomy Picture of the Day via the NASA public API.
    \item Supports date-based browsing with image display and metadata (titles, explanations).
\end{itemize}

\textbf{Edmonds-Karp Algorithm (Java)} \hfill \href{https://github.com/Senaath-Suraweera/NetworkFlow-Edmonds-Karp}{GitHub}
\begin{itemize}
    \item Implemented the Edmonds-Karp algorithm for maximum network flow using BFS-based augmenting path selection.
    \item Achieves O(VE\textsuperscript{2}) complexity with support for directed weighted graphs.
\end{itemize}

\textbf{Dinic's Algorithm (Java)} \hfill \href{https://github.com/Senaath-Suraweera/NetworkFlow-Dinics}{GitHub}
\begin{itemize}
    \item Implemented Dinic's algorithm constructing level graphs via BFS and finding blocking flows using DFS.
    \item Achieves O(V\textsuperscript{2}E) complexity, outperforming Ford-Fulkerson on dense graphs.
\end{itemize}

\textbf{Middleware Architectures (Java)} \hfill \href{https://github.com/Senaath-Suraweera/Middleware-Project-Based-Leaning}{GitHub}
\begin{itemize}
    \item Explored common middleware patterns including message brokers, RPC, and event-driven communication.
    \item Each module demonstrates a different middleware style with practical, runnable examples.
\end{itemize}

\textbf{Ticket Simulation (Java)} \hfill \href{https://github.com/Senaath-Suraweera/Ticket-Simulation}{GitHub}
\begin{itemize}
    \item Built a multi-threaded ticket booking simulation modelling concurrent vendor and customer threads competing for a shared ticket pool.
    \item Demonstrates synchronization, thread safety, and producer-consumer patterns.
\end{itemize}

\textbf{Advanced Ludo Simulation (Java, LWJGL)} \hfill \href{https://github.com/Senaath-Suraweera/Ludo-LWJGL}{GitHub}
\begin{itemize}
    \item Developed a complete Ludo game simulation with structured game logic and interactive CLI interface.
    \item Implemented efficient algorithms for gameplay mechanics and state management.
\end{itemize}

\textbf{Plane Ticket Booking System (Java)} \hfill \href{https://github.com/Senaath-Suraweera/Plane-Ticket-Management-System}{GitHub}
\begin{itemize}
    \item Designed and implemented a seat reservation system using Object-Oriented Programming principles.
    \item Handled booking logic, seat allocation, and user data management.
\end{itemize}

\textbf{2D Arcade Shooter (Java)}\hfill \href{https://github.com/Senaath-Suraweera/Shooter.git}{GitHub}
\begin{itemize}
    \item Built a 2D shooter game from scratch without a game engine.
    \item Implemented collision detection, scoring systems, and real-time gameplay logic.
\end{itemize}

\textbf{Student Progression Predictor (Python)}\hfill \href{https://github.com/Senaath-Suraweera/Progression-Report-Script.git}{GitHub}
\begin{itemize}
    \item Developed a system to predict student outcomes using data analysis techniques.
    \item Visualized results using histograms for better interpretation.
\end{itemize}

\textbf{To-Do Application (C / Python)}\hfill \href{https://github.com/Senaath-Suraweera/Todo-List.git}{GitHub}
\begin{itemize}
    \item Created a task management system using linked lists and file storage (CSV).
    \item Enabled efficient data handling and persistent storage.
\end{itemize}

%-------------------- TECHNICAL SKILLS --------------------
\section*{Technical Skills}

\textbf{Programming:} Java, C, C++, Python \\
\textbf{Web Development:} HTML, CSS, JavaScript, React \\
\textbf{Backend \& Databases:} Spring Boot, Django, SQL \\
\textbf{Tools:} Git, GitHub, MySQL, Notion, ClickUp

%-------------------- SOFT SKILLS --------------------
\section*{Core Competencies}

\begin{itemize}
    \item Problem Solving \& Critical Thinking
    \item Teamwork \& Leadership
    \item Communication Skills
    \item Time Management \& Adaptability
\end{itemize}

%-------------------- EXTRACURRICULAR --------------------
\section*{Extracurricular Activities}

\begin{itemize}
    \item President – Astronomy Society, Mahanama College
    \item President – Buddhist Society, Mahanama College
    \item Member – Rotaract Club of Colombo West
    \item Member – ICT Society
    \item Student Parliament Member \& Junior Prefect
\end{itemize}

%-------------------- INTERESTS --------------------
\section*{Interests}
Music, Weightliftin, chess

%-------------------- REFERENCES --------------------
\section*{References}

\textbf{Prof. A.M. Attygalla} \\
Professor of Maxillofacial Surgery, University of Peradeniya \\
Phone: +94 777 282 993 \\
Email: amattygalla@dental.pdn.ac.lk

\vspace{5pt}

\textbf{Shehan Kumar} \\
Visiting Lecturer, IIT \\
Phone: +94 727 249 324 \\
Email: shehanrk@gmail.com

\end{document}